Measurement of nuclear excitation functions for proton induced reactions (E\texorpdfstring{$_{\text{p}}$\,=\,}{Ep = 40--90}40--90 MeV) on natural Nb

### 2018-04-03 nb_px_paper/nb_px_paper.tex
Finished merging in Lee's final comments.

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium 
% \sep Copper\sep Aluminum 
\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
% Proton activation \sep 
% Proton transport \sep 
Stacked target activation \sep Monitor reactions \sep 
% Monitor foils 
Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
% 
% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)
% 
\end{keyword}

@@

% describe integral equation for converting activities to currents here
% 
% % % 
% 
%  Move these first two commented sentences into PhD thesis.
% 
% % % 
% An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
% At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
% For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
% To this end, 
In addition to direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions have been well-characterized for accurate proton fluence measurement \cite{gul2001charged}.
The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
%by convolving the IAEA recommended cross section values with the proton energy distribution:
% \begin{equation}
% A_0 = I\ \rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE
% \end{equation}
\begin{equation}
I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
\end{equation}
where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy $E$, and $\frac{d\phi}{dE}$ is the differential proton fluence.
Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental data sets used in their evaluation.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
These estimates of average beam energy in each foil are useful for the preliminary stack design, as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering. 
However, for final energy and fluence determinations, a more rigorous method of proton transport is needed.
The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
In addition, MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.  $10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.

@@

Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
Due to the difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to the thick 6061 aluminum degraders (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$).
As such,  the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.

@@

The impact of this variance minimization may  clearly be seen in   \autoref{fig:variance_mins}.
As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0 MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
In both cases, this disparity is caused by the fact that the Kapton tape used for sealing foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.

@@

While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to the number of assumptions involved in such a calculation.
The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
These have been taken as 10\% (stoichiometric basis) and 4.79 mg/cm$^2$ (based on bulk density), respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
In principle, it would be possible  to subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
The results of this  may be seen in \autoref{fig:na_subtraction} --- following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils. 
% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively. 
% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.

@@

An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
In the interest of surety of because they are consistent, the uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport model, as well as an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly more aggressive fluence loss throughout the stack.
These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions. 
%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
  A clear loss of fluence  is visible, dropping by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.  This is due to a combination of beam utilization, as well as scattering.}
 \label{fig:fluence_plot}
\end{figure}

@@

Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged cross sections, over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
For both the cumulative and independent activities quantified, cross sections were calculated as:
\begin{equation}
\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
\end{equation}
where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).

>>>>

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium 
% \sep Copper\sep Aluminum 
\sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep 
% Proton activation \sep 
% Proton transport \sep 
Stacked target activation \sep Monitor reactions \sep 
% Monitor foils 
Medical isotope production \sep Isomer branching ratios \sep  
% Nuclear spin distributions  \sep 
MCNP \sep  LANL
% 
% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)
% 
\end{keyword}

@@

% describe integral equation for converting activities to currents here
% 
% % % 
% 
%  Move these first two commented sentences into PhD thesis.
% 
% % % 
% An accurate integrated proton current is one of the most important factors in performing high-fidelity cross section measurements.
% At the time of this work, the nondestructive beam current monitors in the LANSCE-IPF beamline had a  resolution of 100 nAh.
% For a low-current irradiation such as this work, where a nominal fluence of 200 nAh is desired, additional fluence sensitivity is thus needed to accurately normalize quantified EoB activities into cross sections.
% To this end, 
In addition to direct beam current measurements, thin \ce{^{nat}Al} and \ce{^{nat}Cu} foils were included along with the \ce{^{nat}Nb} targets at each energy position, to provide another beam current monitor.
% These foils have been recommended for use as proton monitor foils in the 30 \textless\ E$_\text{p}$ \textless\ 100 MeV regime by the IAEA, as the
The IAEA-recommended \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions were used for  proton fluence measurement \cite{gul2001charged}.
% The recommended cross section values for each of these reactions were used in all calculations of proton fluence for the above monitor reactions.
Due to the large energy degradation between the front and  back of the target stack, a non-trivial broadening of the proton energy distribution is expected for all monitor and target foils.
As a result, the integral form of the well-known activation equation is used to accurately determine proton fluence ($I \Delta t $) in each monitor foil:
%by convolving the IAEA recommended cross section values with the proton energy distribution:
% \begin{equation}
% A_0 = I\ \rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE
% \end{equation}
\begin{equation}
I \Delta t = \dfrac{A_0 \Delta t}{\rho \Delta r \pp{1-e^{-\lambda \Delta t}} \int \sigma\pp{E} \dfrac{d\phi}{dE} dE}
\end{equation}
where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, $\Delta t$ is the length of irradiation, $\sigma\pp{E}$ is the IAEA recommended cross section at energy $E$, and $\frac{d\phi}{dE}$ is the differential proton fluence.
Using this formalism, the quantified EoB activities for each monitor reaction may be converted into a measured proton fluence at each energy position.

The propagated uncertainty in proton fluence is calculated as the quadrature sum of the uncertainty in quantified EoB activity, uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible), uncertainty in IAEA recommended cross section, and uncertainty in differential proton fluence.
Of these, the first four contributions are all easily quantified in the preparation and execution of a stacked target irradiation;  the last two contributions prove to be more nuanced, however.
The uncertainty in proton fluence for irradiated monitor foils is derived from statistical uncertainty in the modeling of proton transport in the stack irradiation, discussed in \autoref{sec:proton_transport}.
The uncertainty in IAEA recommended cross section values must be estimated indirectly, as no uncertainty in the  recommended cross sections is provided in the current IAEA evaluation.
Fortunately, the recommended cross section values for each monitor reaction tend to closely match one of the   selected experimental source data sets used in their evaluation.
Since these data sets have listed uncertainties in the original manuscripts, uncertainties in  IAEA recommended cross section values have been estimated by the uncertainty in the data set most closely matching the  IAEA recommended  values.
For the monitor reactions employed in this work, these data sets are G. Steyn (1990) for  \ce{^{nat}Al}(p,x)\ce{^{22}Na} \cite{Steyn1990}, M. Uddin (2004) for \ce{^{nat}Al}(p,x)\ce{^{24}Na} \cite{Uddin2004}, and S. Mills (1992) for \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} \cite{Mills1992}.

@@

Initial estimates of the proton beam energy in all foils were calculated using the Anderson \& Ziegler (A\&Z) stopping power formalism \cite{Andersen_Ziegler_1977,Ziegler1985,Ziegler1999}.
These estimates of average beam energy in each foil are useful for the preliminary stack design.
% , as the A\&Z calculations provide reasonable approximations of 1-D proton transport due to treatment of ionization and multiple Coulomb scattering. 
However, for final energy and fluence determinations, a more rigorous method of proton transport modeling is needed.
The Monte Carlo N-Particle transport code MCNP6.1 was used for simulation of the full 3-D target stack, including determination of the full proton energy distribution for each stack position   \cite{Goorley2012}.
% In addition, 
MCNP6 provides a far more robust method of proton transport, as it is able to account for beam losses due to scattering and reactions, as well as production of secondary particles.
As it is a Monte Carlo-based code, the uncertainty in energy distribution scales inversely with the number of source protons simulated.  $10^8$ source protons were used for all simulations, which places the statistical uncertainty in proton energy distributions at less than 0.01\%.

@@

% Variance minimization techniques were employed  to correct for uncertainties in  the characterization of the stack components, the largest cause of uncertainties in energy and  fluence assignments.
Due to the  
% difficulty of characterizing uncertainty in areal density in the Kapton tape, the areal density of these layers were varied uniformly in MCNP6 simulations by up to $\pm$25\% of nominal values.
% This had negligible impact on improving monitor reaction disagreement  due to the small effect that their areal density has on beam degradation relative to 
significantly greater areal density of the thick 6061 aluminum degraders as compared to the other stack elements (nominal 3--5 mg/cm$^2$, relative to nominal 1000--1400 mg/cm$^2$),
% As such
the areal density of each of the 6061 aluminum degraders  were varied uniformly in MCNP6 simulations  by a factor of up to $\pm$25\% of nominal values, to find the effective density which minimized variance in the measured proton fluence at the lowest energy position (Al-6, Cu-6).
This lowest energy position was chosen as a minimization candidate, as it is most sensitive to systematic uncertainties in stack design.
The results of this minimization technique, shown in \autoref{fig:variation_curve}, indicate a clear minimum in proton fluence variance for flux-weighted average 41.34 MeV protons entering the last energy position.
This is approximately 2 MeV lower than the nominal MCNP6 simulations, and approximately 3 MeV lower than nominal A\&Z calculations, both of which used the nominal 2.80 g/cm$^3$ measured density of the 6061 aluminum degraders.
This energy corresponds to a 6061 aluminum areal density of 2.52\% greater than nominal measurements, and serves as a lump correction for other minor systematic uncertainties in stack design, including stack areal densities and incident beam energy.

@@

The impact of this variance minimization is  clearly  seen in   \autoref{fig:variance_mins}.
As expected, the 2.52\% increase in 6061 aluminum areal density has an almost negligible impact on the higher-energy positions, but causes a progressively larger downshift  in proton energies at the later energy positions.
In addition, as one moves to the rear  positions, the disagreement in the independent proton fluence measurements is reduced.
% \comment{Insert text here to describe our Na22 / Si production hypothesis.  }
It is worth noting that the proton fluence measured by the \ce{^{nat}Al}(p,x)\ce{^{22}Na} monitor reaction (threshold 21.0 MeV) is consistently higher in magnitude than all other monitor channels, with an increasing disparity at higher energies.
This phenomenon is observed for the \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor reaction as well (threshold 24.6 MeV), though to a much smaller degree.
In both cases, this disparity is caused by the fact that the Kapton tape used for sealing the foil packets (comprised of a silicone adhesive layer on a polyimide backing) contains a significant amount of silicon, making up approximately 10\% of the silicone on a stoichiometric basis.
\ce{^{22}Na} and \ce{^{24}Na}, the residual nuclei used as monitors, can also be populated off of natural silicon  (92.2\% \ce{^{28}Si}), predominantly via \ce{^{28}Si}(p,$\alpha$2pn)\ce{^{22}Na} (threshold 35.3 MeV) and \ce{^{28}Si}(p,4pn)\ce{^{24}Na} (threshold 44.6 MeV).
\ce{^{29}Si} and \ce{^{30}Si} are also potential targets for (p,x)\ce{^{22,24}Na}, albeit with higher energetic thresholds and smaller cross sections.
In addition, each aluminum foil packet contains approximately 6.5 mg/cm$^2$ of Al, as well as approximately  9.6 mg/cm$^2$ of silicone.
The attribution of excess Al(p,x)\ce{^{22,24}Na} activity to the silicone adhesive is confirmed by the observation of \ce{^{22}Na} and \ce{^{24}Na} activities in all Cu and Nb foil positions.

@@

While these TENDL cross sections simply provide approximate \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} yields,  there are several important  conclusions to be drawn from this quick estimate.
The observation of the \ce{^{22,24}Na} activities in Cu and Nb foils  represents an indirect measurement of the \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, but they will not be reported due to 
% the number of assumptions involved in such a calculation.
uncertainties in the areal density of the Si in the adhesive.
% The EoB \ce{^{22,24}Na} activities have been measured directly, but to convert these into absolute cross sections, accurate knowledge of the precise silicone composition and areal density are required.
% These have been taken as
However, if we assume a 10\% Si stoichiometric basis and an areal density of 4.79 mg/cm$^2$ (based on bulk density),
% respectively, for the purposes of transport calculations, but this level of confidence is insufficient for the reporting of a cross section.
% In principle, it would be possible  to 
we can subtract out the measured \ce{^{22,24}Na} activity at each Nb and Cu foil position (correcting for the minor difference in proton energy between adjacent foils) from the total \ce{^{22,24}Na} apparent activities observed in each Al foil packet, in order to obtain the \enquote{true} or uncontaminated fluence via the aluminum monitor reactions.
The results of this  may be seen in \autoref{fig:na_subtraction}.
Following subtraction, the \ce{^{22,24}Na} fluences become consistent with other monitor reaction channels, within a mere 3--4\% spread.
While this would circumvent the assumptions needed for reporting \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} cross sections, subtraction of  inaccurately quantified \ce{^{22,24}Na} activity in each Nb and Cu foil would propagate into the final fluence determination at each energy position, shifting the magnitude of all reported cross sections.
Even following subtraction, the \ce{^{22}Na} fluence remains 3--6\% higher than the weighted mean of the remaining monitor reaction channels.
While the dramatic improvement in monitor reaction consistency builds confidence, in the interest of surety and because they are consistent, only the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels will be used for fluence determination for the reported cross sections.
% In both cases, this disparity is caused by the fact that both of these monitor reactions may also form the \ce{^{22}Na} and \ce{^{56}Co} reaction products through contamination by secondary neutron (n,x) channels, increasing the apparent fluence as observed by these monitor reactions.
% Since no method for reliably separating the fraction of \ce{^{22}Na} and \ce{^{56}Co} activities induced through (n,x) exists, the fluences predicted by these monitor channels are not used in the final determination of the proton fluence seen by Nb foils. 
% The fact that this \enquote{extra fluence} diminishes at lower energy is likely attributed to the fact that the \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Cu}(p,x)\ce{^{56}Co} have energetic thresholds of 23.35 and 36.76 MeV, respectively. 
% The fraction of secondary neutrons produced by (p,xn)  which are energetic enough to populate the  \ce{^{22}Na} and \ce{^{56}Co} reaction products at the lower energy positions becomes progressively smaller.
This serves as a pointed example of the importance of selecting monitor reaction products inaccessible through channels aside from the primary reaction (\ce{^{nat}Al}(p,x)\ce{^{22,24}Na}, in this case ), as noted previously.
% However,  the fact that both monitor reactions measure consistently higher fluence than the other channels on each foil builds confidence that the monitor reactions accurately indicate the presence of a non-negligible secondary neutron flux.

@@

An enhanced version of the final monitor reaction fluences may be seen in \autoref{fig:fluence_plot}, which shows the   observed fluence of the \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reaction channels.
Without the reliable use of the  \ce{^{nat}Al}(p,x)\ce{^{22}Na} and \ce{^{nat}Al}(p,x)\ce{^{24}Na} monitor channels, local interpolation cannot be used for fluence assignment to the Nb foils, and global interpolation is reliant upon a validated model for fluence loss.
% In the interest of surety of because they are consistent, t
The uncertainty-weighted mean  for the three \ce{^{nat}Cu}(p,x) monitor channels was calculated at each energy position, to determine the final fluence assignments for the Nb and Cu foils.
Uncertainty in proton fluence  is likewise calculated as the error propagation of the fluence values  at each energy position.
These weighted-mean fluences are also plotted in in \autoref{fig:fluence_plot}, along with the estimated fluence according to both the MCNP6 transport 
% model, as well as 
and an uncertainty-weighted linear $\chi^2$ fit to the individual  fluence measurements in each monitor channel.
Both models reproduce the observed fluence data consistently within uncertainty, with the MCNP6 model predicting a slightly greater fluence loss throughout the stack.
These models are used purely to provide an extrapolation from the 90 MeV energy position back to the \enquote{front} of the stack at 100 MeV, to compare with the nominal fluence measured by the IPF upstream current monitors.
% This involved minimizing on $\chi^2$ / degree of freedom, so that  a 95\% confidence interval in fluence would be reported as as well.
% As with the FWHM, a greater than 1$\sigma$ confidence interval is used for reporting fluence uncertainty to avoid an unrealistically small fluence confidence interval, based on the spread in observed fluence from Al and Cu monitor foils.
% The fluence and 2$\sigma$ uncertainties from this weighted-fit line are thus used in calculations of the various Nb(p,x) cross sections

@@

\begin{figure}
 \centering
 \includegraphics[width=0.5\linewidth]{./figures/fluence_plot.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Final uncertainty-weighted mean proton fluences throughout the target stack, based on the variance-minimized observed fluence from the the  \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions. 
%  A 95\% ($2\sigma$) confidence interval is reported in the fitted proton fluence, to ensure a realistic uncertainty in fluence, which encompasses the true absolute fluence. 
%   A clear loss of 
  The fluence  drops by approximately 7.2--8.9\% from the incident fluence of 196.9--198.8 nAh over the length of the target stack, based on fluence loss models from MCNP6 simulations and an empirical fit to  fluence measurements.}  
%   This is due to a combination of beam utilization, as well as scattering.}
 \label{fig:fluence_plot}
\end{figure}

@@

Using the quantified EoB activities along with the variance-minimized proton fluence, it is possible to calculate the final cross sections for the various observed Nb(p,x) reactions.
While thin ($\approx$ 22 mg/cm$^2$) Nb foils were irradiated to minimize the energy width of these cross section measurements, it is important to note that all cross sections reported here are flux-averaged  
% cross sections, 
over the energy distribution subtended by each foil, as seen in \autoref{fig:Nb_ptallies}.
For both the cumulative and independent activities quantified, cross sections were calculated as:
\begin{equation}
\sigma = \dfrac{A_0 }{\rho \Delta r I \pp{1-e^{-\lambda \Delta t}} }
\end{equation}
where $A_0$ is the EoB activity for the monitor reaction product, $I$ is the proton current, $\rho \Delta r$ is the foil's areal density, $\lambda$ is the monitor reaction product's decay constant, and $\Delta t$ is the length of irradiation.
The beam current, measured using an inductive pickup, remained stable for the duration of the irradiation, with the exception of approximately 70\,s of downtime,  occurring approximately 3 minutes into irradiation.
The propagated uncertainty in cross section is calculated as the quadrature sum of the uncertainty in quantified EoB activity (which includes uncertainty in detector efficiencies), uncertainty in the duration of irradiation (conservatively estimated at 60 s, to account for any transient changes in beam current), uncertainty in foil areal density, uncertainty in monitor product half-life (included, but normally negligible),  and uncertainty in proton current (quantified by error propagation of the monitor reaction fluence values  at each energy position, as seen in \autoref{fig:fluence_plot}).
